\documentclass[10pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\setcounter{secnumdepth}{0}
%
\title{\Huge Assignment 3}
\begin{document}
	\begin{titlepage}
		\maketitle
		\begin{center}
			\large Introduction to Information Technology\\
			\vspace{12cm}
			\author{Levin Alexander, Reilly Andrews, Mark Baptista, Liam Farley and Rohit Menon}
		\end{center}
	\end{titlepage}
\tableofcontents
\pagebreak
\section{Team Profile}
\Large Team Name: Silicone Spiders
\normalsize
\subsection{Personal Information}
\subsubsection{Rohit Menon \textbar\hspace{0.4mm}  S3544222 }
I was born in Mumbai, India. I left india when I was just a year old and moved to Dubai, where I spent the next 9 years of my life. After this I moved to Melbourne and have grown up and studied here ever since. I always have been passionate about IT, and have great interest in web development and graphic design. I also have experience in IT, working as a freelance web and graphic designer for various businesses and organisations. Some of my hobbies include playing the guitar, graphic design and macro photography.
\subsubsection{Levin Alexander \textbar\hspace{0.4mm}S3514587}

I was born and brought up in Singapore. Did my Primary and High School in Singapore. Came to Australia in 2015 to pursue Diploma in Information Technology and Bachelors in Information Systems. Since young I have always been passionate in learning IT. When I started doing my Diploma, that is when I realised that Coding and Creating Websites interests me alot. As of now, I don’t have any experience in IT, apart from the fact that I did Diploma in IT. Apart from IT, I love playing games and soccer during my free time.
\subsubsection{Mark Baptista \textbar\hspace{0.4mm}S3722699}
I was born in Melbourne, Australia in August of 1999, I have spent all of my life living in Melbourne including my education from the Preparatory year to VCE units 3/4 (Year 12). From an early age Information technology has been my passion funneling through to an interest in programming and UX design, however, my past experiences in IT have only been in my VCE computing units. Some other things that I am interested in are: Gaming, Sports and Music.
\subsubsection{Reilly Andrews \textbar\hspace{0.4mm}S3717650}
My name is Reilly Andrews, I was born in Australia and I’m currently studying I.T at the University of RMIT. I enjoy playing video games and have a strong passion for reading and writing as well; I also love synth music. My I.T interests include things such as programming and learning how computer systems and hardware work. I currently have no real experience in the I.T field, however I’m hoping that will change in the future!
\subsubsection{Liam Farley \textbar\hspace{0.4mm}S3600296 }	
My name is Liam Farley, i am from a town called Warrnambool but have moved up to melbourne for university. The course i am doing is Information Technology at RMIT. My hobbies are anything to keep active and movies. My I.T interests include backend coding whether it be for software, websites, games. I also really enjoy website development. I have experience in website development where i have created a fully functional website for a Crane Hire business in Warrnambool. 
\subsection{Group Processes}
\subsection{Career Plans}
\section{Tools}
\section{Project Description}
\section{Overview}
\section{Detailed Descriptions}

\end{document}